Quality Metrics for SKOS Vocabularies

### 2012-03-11 analysis.tex
added vocab table draft

\subsection{Vocabulary Data Set}

\todo{CM}{Add dataset table so that we know how much space this will take.}
\begin{table}[h]
\caption{Analyzed vocabularies}
\begin{tabular}{|p{2.5cm}|p{6cm}|p{2cm}|p{.5cm}|p{.5cm}|p{.5cm}|p{.5cm}|p{.5cm}|}
\hline
\textbf{Domain} & \textbf{Vocabulary} & \textbf{CO} & \textbf{LR} & \textbf{SR} & \textbf{AR} & \textbf{CS} & \textbf{CL}\\
\hline
Media & GTAA & & & & & & \\
\hline
Science & Geonames Ontology &&&&&& \\
\hline
& MeSH &&&&&& \\
\hline
& Peroxisome Knowledge Base &&&&&& \\
\hline
Government & Eurovoc &&&&&& \\
\hline
& IPSV &&&&&& \\
\hline
\\
\hline

>>>>

\subsection{Vocabulary Data Set}
\todo{CM}{add info about data gathering process and vocab changes/fixes to parse them}
\begin{table}[h]
\caption{Analyzed vocabularies}
\begin{tabular}{|p{2cm}|p{6cm}|p{1.5cm}|p{.8cm}|p{.8cm}|p{.8cm}|p{.8cm}|p{.8cm}|}
\hline
\textbf{Domain} & \textbf{Vocabulary} & \textbf{CO\footnote{concepts}} & \textbf{LR\footnote{lexical relations}} & \textbf{SR\footnote{semantic relations}} & \textbf{AR\footnote{associative relations}} & \textbf{CS\footnote{concept schemes}} & \textbf{CL\footnote{collections}}\\
\hline
Media & GTAA & & & & & & \\
\hline
Science & Geonames Ontology &&&&&& \\
\hline
& MeSH &&&&&& \\
\hline
& Peroxisome Knowledge Base &&&&&& \\
\hline
Government & Eurovoc &&&&&& \\
\hline
& IPSV &&&&&& \\
\hline
Publications & Agrovoc &&&&&& \\
\hline
& DBpedia Categories &&&&&& \\
\hline
& Pressinfo &&&&&& \\
\hline
& NYT people &&&&&& \\
\hline
& LCSH &&&&&& \\
\hline
Cross-domain & Meketre &&&&&& \\
\hline
Economy & STW &&&&&& \\
\hline
& NAICS &&&&&& \\
\hline
Military & LVAk &&&&&&
\\
\hline
